---
output:
  html_document: default
  pdf_document: default
---

```{r, message=FALSE, echo=FALSE}
library(ggplot2)
library(dplyr)
library(moderndive)
#Import Data
df <- read.csv("STT-3850-101 Project Data - Form Responses 1.csv")
# Rename columns
colnames(df) <- c("time","major","year","water","nonwater")
# Delete timestamp
df <- subset(df, select = -c(time))
df <- df %>%
  mutate(nonwater = nonwater / 7)

# Consolidate the data
new_data <- df %>%
  mutate(upper = ifelse(year == "Freshman" | year == "Sophomore", "lower", "upper")) %>%
  mutate(major = ifelse(major == "College of Fine and Applied Arts" | major == "Hayes School of Music", "College of Fine and Applied Art/Hayes School of Music", major))

# Trim old columns
new_data <- new_data %>%
  select(major, upper, water, nonwater)
```

# Survey on Water vs Beverages Consumed by Major and Years at AppState

#### Nova Doolittle

#### Clayton-George Reid 

------------------------------------------------------------------------

### Exploratory Analyses

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = new_data, aes(x = water, y = nonwater)) +
  geom_point() +
  #geom_jitter() +
  # Remove the 100 cups of water/day outlier
  xlim(0, 25) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  labs(x = "Water Intake (cups) per Day",
       y = "Mean number of beverages (by 'drink') per Day",
       title = "Day Water Intake vs. Weekly Beverage Intake")
```

To see if our data was at least logical, we first plotted the linear relationship between water and beverages. The assumption is that, given a finite amount of time in the day, there could be no way to consume, say, 15 cups of water (nearly a gallon) a day and still have time to drink 7 beverages (soda, juice, alcohol, etc.).

We see a generally negative linear relationship between the two variables.

```{r, message=FALSE, echo=FALSE}
water_nonwater_model_year = lm(water ~ nonwater, data = new_data)
get_regression_table(water_nonwater_model_year)
```

This is the same plot, but now separated by upper/lower classmen. While both trend downward, we find that upper-classmen tend to drink more beverages than their lower-classmen peers.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = new_data, aes(x = water, y = nonwater, color = upper)) +
  geom_point() +
  #geom_jitter() +
  # Remove the 100 cups of water/day outlier
  xlim(0, 25) +
  labs(x = "Water Intake (cups) per Day",
       y = "Mean number of beverages (by 'drink') per Day",
       color = "Upper Classmen",
       title = "Day Water Intake vs. Weekly Beverage Intake") +
  geom_parallel_slopes(se = FALSE)

```

```{r, message=FALSE, echo=FALSE}
upper_water_nonwater_model = lm(water ~ nonwater + upper, data = new_data)
get_regression_table(upper_water_nonwater_model)
```
